Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes

### 2015-09-01 papers/ellicular/ellicular.tex
balayage

\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their supermassive black holes}

@@

\begin{abstract}
vjsfkajhda
\end{abstract}

@@

A thorough review can be found in \citet{combes2014arX} and \citet{combes2014pro}.

@@

as their nuclear and large-scale homologues, 
or, in some cases, they have even been labelled as something ''unphysical''. 

@@

However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modelers, 
who have labeled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 

@@

\section{Galaxies}
\label{sec:gal}
Three examples of early-type galaxies with intermediate-scale discs are NGC 3115, Mrk 1216, and NGC 1271. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis (when) available from the literature. 
For the galaxy NGC 3115, we used a $3.6~\rm \mu m$ image obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxies Mrk 1216 and NGC 1271, we used archived Hubble Space Telescope (\emph{HST}) images 
taken with the Wide Field Camera 3 (\emph{WFC3}) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized for each individual image 
using a Gaussian or a \cite{moffat1969} profile.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated
by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{isofit...} \citep{taskellipse}. 
The galaxy isphotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (see Figure \ref{fig:n3115}). 
Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
However, the ellipticity profile is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 disprove the presence of a large scale disc, 
because the galaxy is rapidly rotating only within two effective radii ($\sim 2 \times 50~\rm arcsec$), 
whereas the rotation significantly drops at larger radii \citep{arnold2011n3115}.  
The unsharp mask (Figure \ref{fig:n3115}) of NGC 3115 betrays the presence of a fain edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).

Two examples of ellicular galaxies are Mrk 1216 and NGC 3115. 
While the presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure 3), 
the disc in Mrk 1216 is not immediately apparent from the image 
-- which is partly why many stellar discs have been over-looked to date. 
However the radial light profile and the ellipticity profile betray the presence of a disc in both galaxies. 
The radial light profiles of Mrk 1216 and NGC 3115 extend out to almost four times (4 x 7 arcsec) 
and five times (5 x 50 arcsec) the galaxy half-light radii, respectively. 
The main distribution of light in both of these galaxies is well described with a S\'ersic function22 
for the spheroidal component plus an exponential function for the intermediate-sized disc. 
Moreover, our photometric analysis enables the recovery of an additional nuclear disc in Mrk 1216 
and a nuclear ring in NGC 3115. 
The spheroid/disc decomposition for NGC 3115 is also in excellent agreement with the galaxy's kinematic properties23. 
This comparison cannot be made for Mrk 1216 because no extended kinematic data are available.  
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the kinematic maps15 (when available) 
and the ellipticity profiles, of three other ellicular galaxies 
for which a direct measurement of their central supermassive black hole mass is available: 
NGC 1271; NGC 1277; and NGC 1332.  
Past models that ``forcedly'' described these ellicular galaxies with an inner bulge 
encased within a large-scale disc 
typically required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) reduce the spheroid luminosity by a factor of 2-3, 
and underestimate the size of the spheroid by a factor of 10.

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{}
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
\caption{}
\label{fig:m1216}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1271_image}
\includegraphics[width=0.49\columnwidth]{images/n1271_unsharp} \\
\includegraphics[width=1.05\columnwidth]{images/n1271_decomposition.pdf}
\caption{}
\label{fig:m1216}
\end{center}
\end{figure}

\section{Implications}
\label{sec:impl}

\subsection{mm diagram}
Obviously, having both the black hole mass and the spheroid mass correct is important 
for placing systems in the (black hole mass)-(spheroid stellar mass) diagram. 
For early-type galaxies, the spheroid luminosity and the total galaxy luminosity 
can be used to predict the black hole mass with the same level of accuracy \citep{savorgnan2015}. 
If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
but whose mass is normal compared to expectations from the total galaxy luminosity, 
one should wonder whether the spheroid luminosity might have been underestimated 
due to an inaccurate spheroid/disc decomposition. 
Indeed, none of the five ellicular galaxies mentioned here is a noticeable outlier 
in the (black hole mass)-(total galaxy luminosity) diagram \citep{savorgnan2015}. 
For the first time, Figure 4 reveals that when ellicular galaxies are properly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram.

\subsection{compact massive sph}
Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ''in-situ'' and ''ex-situ''. 
The first phase takes place in a young Universe (within its first 4 billion years), 
when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
These naked and compact cores, named ''red nuggets''25, have been observed26 at high-redshift with sizes of 1-2 kpc.
In the second phase (last 10 billion years), stellar discs and stellar envelopes 
were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of 2-20 kpc. 
Today's Universe is populated by an abundance of compact, massive spheroids27, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies. 
Over the last 10 billion years their spheroids have evolved by growing a relatively flat disc -- 
rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
with purely old (>10 billion years) stellar populations. 
These galaxies have undergone the lowest degree of disc growth.
In addition to the observational clues as to the actual physical components in ellicular galaxies, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope5,28,6. If they were such three-component systems, 
then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled 10 billion years ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first 4 billion years of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of 0.1-0.2 kpc, 
according to past decompositions) originated in the first 4 billion years 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are 10 times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact (1-2 kpc). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact ellicular galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact ellicular galaxy quickly assembled ''in-situ'' in a very young Universe 
and experienced very little evolution over the last 10 billion years.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/mm.pdf}
\caption{Early-type galaxies: black hole mass plotted against spheroid stellar mass for 42 galaxies (black) plus the galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, and NGC 4291. The black solid line is the bisector linear regression for early-type galaxies24. The dashed lines mark the 1sigma and 3sigma deviations, where sigma (0.51 dex) is the total rms scatter about the correlation in the black hole mass direction. The red color is used for five ellicular galaxies, (Mrk 1216, for which only an upper limit on its black hole mass has been reported) [4], NGC 1271 [6], NGC 1277 [5, 4], NGC 1332 [7], and NGC 4291 [29]), that were claimed to be extreme outliers in this diagram. All reside within a 3sigma deviation from the correlation when using their correct spheroid mass. For NGC 1277, we show the previously reported spheroid stellar mass [5] in gray.}
\label{fig:mm}
\end{center}
\end{figure}

@@

\section{Acknowledgments}
%GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
% referee thank you!!
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
%This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
%on-board the Spitzer Space Telescope, 
%which is operated by the Jet Propulsion Laboratory, 
%California Institute of Technology under a contract with NASA.
%This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
%which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
%under contract with the National Aeronautics and Space Administration.

>>>>

\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}

@@

\begin{abstract}
The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
However, several studies only consider spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
with intermediate-scale disc. 
Intermediate-scale discs have often been confused with large-scale discs, 
and as a consequence the disc luminosities have been considerably overestimated 
and their spheroid luminosities underestimated. 
%intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
%Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
%and their spheroid luminosities underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of intermediate-scale disc galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
When intermediate-scale disc galaxies are properly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
thereby resolving previous anomalies. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

\end{abstract}

@@

A thorough review can be found in \citet{combes2014arX,combes2014pro}.

@@

as their nuclear and large-scale homologues and,  
in some cases, they have even been labelled as something ''unphysical''. 

@@

However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modellers, 
who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of early-type galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis (when) available from the literature. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available.} \citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
whereas the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
The surface brightness profile (Figure \ref{fig:n3115}) is well described with a S\'ersic-spheroid \citep{sersic1963},  
an intermediate-sized exponential-disc, and a Gaussian-ring.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component was identified from our photometric analysis. 
The authors of this paper were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because possibly affected by the presence of a partially depleted core.
The spheroidal component of NGC 1332 is modelled with a S\'ersic profile. 
The highly inclined intermediate-scale disc is better described with a $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function \citep{pastrav2013a}. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$.
\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
In Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies.

\subsection{Mrk 1216}
Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} proves the presence of a fast rotating component 
at least within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}) indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$) 
and from a clear feature in the fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

\subsection{Other galaxies}
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
of other galaxies for which a direct measurement of their central supermassive black hole mass is available: 
NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(\emph{in prep.}), respectively, 
while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (\emph{submitted}).

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{The galaxy NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{The galaxy NGC 1332. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit.   
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
\caption{The galaxy Mrk 1216. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:m1216}
\end{center}
\end{figure}

\section{Implications}
\label{sec:impl}
Past models that ``forcedly'' described intermediate-scale disc galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found. \\
\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.

\subsection{The black hole -- spheroid correlation}
\label{sec:mm}
Inaccurate measurements of the spheroid-to-total ratio of galaxies can impact galaxy scaling relations. 
Recently, a handful of intermediate-scale disc galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 
i.e.~their central supermassive black hole has been reported to be 
over-massive compared to expectations from the spheroid luminosity (or stellar mass).
This is the case for the galaxies Mrk 1216 (for which only an upper limit on its black hole mass has been published, 
\citealt{yildirim2015}), NGC 1271 \citep{walsh2015}, 
NGC 1277 \citep{vandenbosch2012,yildirim2015} and NGC 1332 \citep{rusli2011}.
In addition to these, also the elliptical galaxy NGC 4291 has been claimed to be a $\sim$$3.6\sigma$ outlier 
above the (black hole mass)-(spheroid mass) scaling relation \citep{bogdan2012}. 
Obviously, having both the black hole mass and the spheroid mass correct is important 
for placing systems in the (black hole mass)-(spheroid mass) diagram. 
For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
can be used to predict the black hole mass with the same level of accuracy\footnote{However, 
when considering all galaxies (early- and late-type) irrespective of their morphological type, 
the correlation of the black hole mass with the spheroid luminosity is better than that with the galaxy luminosity.} 
(Savorgnan et al.~\emph{submitted}). 
If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
but whose mass is normal compared to expectations from the galaxy luminosity, 
one should wonder whether the spheroid luminosity might have been underestimated 
due to an inaccurate spheroid/disc decomposition. 
Indeed, none of the five galaxies mentioned before (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 
in the (black hole mass)-(galaxy luminosity) diagram. 
In Figure \ref{fig:mm} we show the location of these five galaxies in the (black hole mass)-(spheroid stellar mass) diagram 
for early-type galaxies of Savorgnan et al.~(\emph{submitted}). 
Figure 4 was populated using a galaxy decomposition technique extensively described in Savorgnan \& Graham (\emph{submitted}). 
Briefly, we obtained Spitzer/IRAC $3.6~\rm \mu m$ images for 45 early-type galaxies 
which already had a dynamical detection of their black hole mass. 
We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, using one function per galaxy component. 
Spheroid luminosities were converted into stellar masses using individual, but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). 
In addition, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, which were not a part of the original sample of 45.
For the galaxy NGC 1271, we use the black hole mass measurement and the mass-to-light ratio obtained by \cite{walsh2015}. 
The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 
For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 
and the mass-to-light ratio obtained by \cite{martinnavarro2015}. 
The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
For the galaxy Mrk 1216, we use the upper limit on the black hole mass and the mass-to-light ratio obtained by \cite{yildirim2015}. 
The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
For the first time, Figure \ref{fig:mm} reveals that when these five galaxies are properly modeled, 
they no longer appear as extreme outliers above the (black hole mass)-(spheroid stellar mass) correlation for early-type galaxies, 
i.e.~they all reside well within a $3\sigma$ deviation from the correlation.

{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

\subsection{Origin of compact massive galaxies}
Acknowledging the correct structure of intermediate-scale disc galaxies is also important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
These naked and compact cores, named ``red nuggets'' \citep{damjanov2009}, have been observed at high-redshift with sizes of $1-2~\rm kpc$ \citep{vandokkum2008}.
In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of $2-20~\rm kpc$. 
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies. 
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc -- 
rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
The other compact massive spheroids of today's Universe belong to some intermediate-scale disc galaxies. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact galaxies 
with intermediate-scale discs and purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in ellicular galaxies, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of $0.1-0.2~\rm kpc$, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact ellicular galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact ellicular galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/mm.pdf}
\caption{Early-type (elliptical + lenticular) galaxies: 
black hole mass plotted against spheroid stellar mass for 48 galaxies. 
The black solid line is the bisector linear regression for all galaxies except Mrk 1216, NGC 1271 and NGC 1277. 
The dashed lines mark the $1\sigma$ and $3\sigma$ deviations, 
where $\sigma$ ($0.51$ dex) is the total \emph{rms} scatter about the correlation in the black hole mass direction. 
The red stars mark four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291) 
that were claimed to be extreme outliers in this diagram. 
All five reside within a $3\sigma$ deviation from the correlation when using their correct spheroid mass. 
For NGC 1277, we show the previously reported spheroid stellar mass \citep{vandenbosch2012} in gray. 
The green color is used to show the location of four other intermediate-scale disc galaxies mentioned in Section \ref{sec:impl}.}
\label{fig:mm}
\end{center}
\end{figure}

@@

\section{Acknowledgments}
% referee thank you!!
This research was supported by Australian Research Council funding through grant FT110100263. 
GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC-MNRAS} on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA, 
and also on observations made with the NASA/ESA Hubble Space Telescope, 
and obtained from the Hubble Legacy Archive, 
which is a collaboration between the Space Telescope Science Institute (STScI/NASA), 
the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.
